---
title: "Crime and Fire Clustering - Presentation and Documentation"
author: 'N'
date: "October 15, 2018"
output:
  ioslides_presentation: default
font_adjustment: -1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## London (UK) Crime and Fire Statistics
```{r plotly, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
```
<font size="1">This Application aims to find links between various Crime and Fire rates by Postal Sector for London, United Kingdon.  The functionality of the app then allows for clustering of the two-way variable to create a new summarised predictive variable in other modelling applications.

As a summary of the app:

 1. Interactive Plot of the factors using Plotly
 2. As above, but on a log scale to improve readability
 3. Visual representation of the K-means clusters with coloured points
 4. As above, but in log scale to improve readability
 5. An export page to output the cluster KPIs by postal Sector (e.g. "SE1 9")
  
On the main screen is a panel with the two way selection of variables and a setting for the number of clusters to produce.

Under the heading is a link to this documentation and the performance measure of the current cluster (total deviance within clusters divided by total deviance of the data).
</font>

## Data and Sources
<font size="1">
The process for producing the data is not provided in a reproducible format due to the requirement for a propriarary UK Map shape file and information on the number of Households present in each UK post sector.  

Some data are in Easting/Northing and need to be projected to Latitude/Longitude (*latlong = "+init=epsg:4326"*) using "spTransform" function.

The UK Shape File is a propriatary shape file (google Superppro data to find the proprioter)
```R63_SuperPro_Postcode_Sectors_SHA.zip```

The data are loaded as Easting/Northing and the .prj file can be obtained as below:
``` OSGB<-"+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +ellps=airy +datum=OSGB36 +units=m +no_defs"```

Monthly Crime KPIs read from https://Police.uk website and loaded from monthly files as below for example:  
#2018-07-metropolitan-street.csv
#2018-07-city-of-london-street.csv

Dwelling fires data for Londong at Easting,Northing (X,Y) coordinates which need to be transformed to Lat/Long and projected:
"https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/738425/domestic-appliance-fires-datatset.ods" </font>
</font>
  
## Available Data/KPIs
<font size="1">
All avilable Crime and Fire KPIs have been produced.  The are normalised by the number of households per Post Sector with a nominal input of 14 (the sector average)  for post sectors with Zero households to ensure that there are not large outputs in the KPIs.

Factors (All KPIs are the Number of recorded incidents per Household)

 - antiSoc_hh:         Anti Social Behaviour
 - bikeTheft_hh:       Bike Thefts
 - burglary_hh:        Burglaries
 - damageAndArson_hh:  Damage and Arsons
 - drugs_hh:           Drug offences
 - other:              Other criminal offences
 - theft:              Other Thefts
 - publicOrder:        Public Order Offences
 - robbery:            Robberies
 - shoplifting:        Shoplifting
 - theftPerson:        Theft from the Person
 - vehicleCrime:       Vehicle Crime/Damage
 - violence:           Violent Attacks
 - weapons:            Weapons Offences
 - totalCrimes_hh:     TOTAL CRIMES RECORDED
 - fire_hh:            Fires
 - falseAlarm_hh:      False Alarms
 - specialService_hh:  Special Service Fire Responses
 - totalFires_hh:      TOTAL FIRES RECORDED
 
</font> 

##Using the Tabs
### Tabs 1-4: Description
<font size="1">
Tabs 1 and 2:

 - These tabs contain interactive plotly charts of the selected KPIs in the drop down on the master page.  
 - There are labels on the points and the size of the marker is representative of the number of reported households in the sector to give some credibility to the KPI presented
 - You can zoom and select the points to make them more readable

Tabs 3 and 4:

 - These show the output of the K means clusters
 - The data points are also plotted and are coloured to show the clustering of the data
 - Although a measure of clustering precision is presented in the main panel (out of 100%) a visual review of the clusters or performance testing on external data is a better option to determine the optimum number of clusters.
 
</font> 

### Tabs 5: Exporting the Cluster
<font size="1">
Tab 5:

 - This tab will output the current cluster by COM_SECT in order to be used in further analyses (e.g. Modelling house prices or insurance claims etc).
 - When clicking the button, you can name your output file and chose the output file location.

Be sure to finish your file name with ".csv" e.g. "Output.csv" as it will make it easier to read the output of your cluster.
</font> 

